---
title: "EDAV Fall 2019 PSet 5, part A"
author: "Yuge Shen, Shengqing Xia, Zhanming Zhang, Zihe Wang"
output:
  pdf_document: default
  html_document: default
---
```{r, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, echo = TRUE)
```

This assignment is designed to help you get started on the final project. Be sure to review the final project instructions (https://edav.info/project.html), in particular the new section on reproducible workflow (https://edav.info/project.html#reproducible-workflow), which summarizes principles that we've discussed in class.
    
### 1. The Team

[2 points]

a) Who's on the team? (Include names and UNIs) 

Yuge Shen - ys3280

Shengqing Xia - sx2230

Zhanming Zhang - zz2699

Zihe Wang - zw2624

b) How do you plan to divide up the work? (Grading is on a group basis. The point of asking is to encourage you to think about this.)

Since we intend to use HTML as the output format, we plan to divide our work this way.

We design the output visualization together.

Code the main graph : Yuge Shen, Zhanming Zhang

Add interactions and other layout features : Zihe Wang, Shengqing Xia


### 2. The Questions

[6 points]

List three questions that you hope you will be able to answer from your research.

a) Will high tobacco tax influence the amount of cigrette consumption?

b) Are people with lower education level tends to smoke more cigrettes?

c) Are "poorer' people tends to smoke more?

### 3. Which output format do you plan to use to submit the project? 

[2 points]

(You don't have to use the same format for this assignment -- PSet 5, part A -- and the final project itself.)

Choices are:

pdf_document  

html_document  

bookdown book: https://bookdown.org/yihui/bookdown/

shiny app: https://shiny.rstudio.com/  


(Remember that it's ok to have pieces of the project that don't fit into the chosen output format; in those cases you can provide links to the relevant material.)

We are considering html right now since we might have an interactive map.

### 4. The Data

[5 points]

What is your data source?  What is your method for importing data? Please be specific. Provide relevant information such as any obstacles you're encountering and what you plan to do to overcome them.

We get most of our data from Centers for Disease Control and Prevention (CDC) and also get the economic data from Bureau of Labor Statistics. There are csv files that we could download directly from the first website. For the second website, although we don't have a csv file, since we only need a few data from it, we just copy and paste the data.

https://nccd.cdc.gov/STATESystem/rdPage.aspx?rdReport=OSH_State.CustomReports
https://www.bls.gov/data/#unemployment



### 5. Provide a short summary, including 2-3 graphs, of your initial investigations. 

[10 points]
The first plot shows whether the state would be a variable which influence the trends of tobacco's tax ranging from 1970 to 2019. We can see that most of the states fluctuated in a similar pattern, while there were 3 states had extremely high value in year 1984, 1989 and 1993. So we may focus on these extreme cases and try to figure out what was benhind the data and what happened in that 3 years.
```{r }
library(ggplot2)
tb = read.csv('TobaccoTax.csv', header = TRUE)
ggplot(data = tb, aes(x = Year, y = Data.Value, color = Location.Description)) +
  geom_line() +
  ggtitle("Tax by States and Years") 
```

The second plot shows that variable 'Response' had the most missing values. And there were only 2 missing patterns, while the most frequent one was missing only 'Response' data.
```{r }
library(naniar)
library(tidyverse)
library(ggplot2)
library(extracat)
library(mi)
library(dplyr)
library(ggmosaic)
library(tidyquant)
library(usmap)
cg = read.csv('./TobaccoUse.csv',na.strings = "*")

visna(cg)
```

```{r}
cg = cg %>% replace_with_na_at(.vars = c("Data.Value"), condition = ~.x %in% ("*"))
```
We want to figure out how people's education level will influence the amount of cigarette they smoke. As the boxplot shown, people with education level less than 12 grades had the highest medium value of tobacco use, moreover, the 25 percentile of them was much larger than the 75 percentile of people with education level higher tha 12 grades, which suggests that there is a realtionship between education level and the use of cigarette that people with lower education level tended to smoke more.
```{r}
ggplot(data = cg, aes(x = Education, y = Data.Value)) + 
  geom_boxplot() +
  ggtitle("Use of Tobacco vs Education Level")
```

Furthermore, we want to discuss whether "poorer' people tends to smoke more and if there is a negative relationship between tobacco tax and the amount of cigrette consumption.


